---
title: "Bee Home Larva"
author: "Katherine Lunn"
date: "2024-11-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(pscl)
library(MASS)
```

## Negative binomial

The impact of sample size on the number of genera identified was considered using a negative binomial regression. 
Target region, sample size and interaction between these were considered as factors which impact the number of genera identified in the samples.

neg_binomial <- glm.nb(ASVs ~ Sample.size * Target.region)

When samples are received add in target_region used. Change from read matrix to binary matrix. 
I would then have to merge all sample names (they will differ between MiSeq runs) so I can create one large document
So that sample size could be identified, I would need to ID bee occupant and then apply that to the sample name

- Can I then run a negative binomial on this? Or do I have to make a summary document?

```{r nbr}
# Bring in All_species_sample_counts_1.csv
beelarva_matrix <- read.csv(file.choose())

neg_binomial <- glm.nb(ASVs ~ Sample.size * Target.region, data = beelarva_matrix)
summary(neg_binomial)
```

## MCA

Multiple correspondence analysis?
- Is there a large difference in the resources utilised by species/groups/areas etc?
Network analysis?
- Can consider whether certain resources are being used more regularly by bee home species than others?


```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
